---
title: "NumberOfClusters"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Computing the indexes por different m values and a given number of realizations

Data for age greater than 60. We are testing the optimum cluster number to optimize fuzzy c-means clustering 

First we have to import the data with the multi correspondence analysis done and the script to compute the fuzzy cmeans indexes to validate the optimum number of clusters

```{r loading, cache=FALSE,echo=TRUE}
setwd("X:\\Analysis internship\\GitHub/")
# setwd("C:\\Users\\Albert.Roso\\Dropbox\\Albert_Roso_internship\\ARC\\Baseline")
load("PCAmix_BL.RData")
source('indexes.R')
# source('C:\\Users\\Albert.Roso\\Dropbox\\Albert_Roso_internship\\indexes.R')
dim(data)
head(data)
library(ggplot2)
library(plyr)
library(dplyr)
library(doSNOW)
```

Especifying the number of realizations and number of clusters and parallelization
```{r setting, cache=FALSE,echo=TRUE}
realizations <- 100
number.clusters <- 2:20
pca <- data

cl<-makeCluster(16)
registerDoSNOW(cl)
set.seed(123)
```

## Indexes computation for different m values

# m=1.1 (A low value, similar to k-means distribution)
```{r m=1.1, cache=TRUE,echo=TRUE}
indexes.m1.1 <- indexes(pca,number.clusters,realizations,m=1.1) 
```

# m=1.2 
```{r m=1.2, cache=TRUE,echo=TRUE}
indexes.m1.2 <- indexes(pca,number.clusters,realizations,m=1.2) 
```

# m=1.4 
```{r m=1.4, cache=TRUE,echo=TRUE}
indexes.m1.4 <- indexes(pca,number.clusters,realizations,m=1.4) 
```

# m=1.5 
```{r m=1.5, cache=TRUE,echo=TRUE}
indexes.m1.5 <- indexes(pca,number.clusters,realizations,m=1.5) 
```

# m=2 (Typical value)
```{r m=2, cache=TRUE,echo=TRUE}
indexes.m2 <- indexes(pca,number.clusters,realizations,m=2) 
```

# m=4 (A large value)
```{r m=4, cache=TRUE,echo=TRUE}
indexes.m4 <- indexes(pca,number.clusters,realizations,m=4) 
```

# Save data
```{r m=4, cache=TRUE,echo=TRUE}
save.image("Indexes_data_BL.Rdata")
```