---
title: "Index Result Plot"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Plotting the different indexes for cmeans

Data for age greater than 65. We are testing the optimum cluster number to optimize fuzzy c-means clustering 

First we have to import the required packages and the index data

```{r loading, cache=FALSE,echo=FALSE}
library(ggplot2)
library(plyr)
library(dplyr)

setwd("X:\\Analysis internship\\GitHub/")
# setwd("C:\\Users\\Albert.Roso\\Dropbox\\Albert_Roso_internship\\ARC")
load("Indexes_data_BL.Rdata")
dim(data)
head(data)
```


## Fukuyama index
Optimum Fukuyama index has to be minimum
```{r fukuyama, cache=FALSE}

fukuyama.dataframe.m1.1 <- ldply(indexes.m1.1$fukuyama.ave)
fukuyama.dataframe.m1.2 <- ldply(indexes.m1.2$fukuyama.ave)
fukuyama.dataframe.m1.4 <- ldply(indexes.m1.4$fukuyama.ave)
fukuyama.dataframe.m1.5 <- ldply(indexes.m1.5$fukuyama.ave)
fukuyama.dataframe.m2 <- ldply(indexes.m2$fukuyama.ave)
fukuyama.dataframe.m4 <- ldply(indexes.m4$fukuyama.ave)



#Options to plot the comparisons per m

ggplot() + geom_line(aes(color="m=1.1",x=number.clusters,y=fukuyama.dataframe.m1.1$V1)) +
  geom_line(aes(color="m=1.2",x=number.clusters,y=fukuyama.dataframe.m1.2$V1))+
  geom_line(aes(color="m=1.4",x=number.clusters,y=fukuyama.dataframe.m1.4$V1))+
geom_line(aes(color="m=1.5",x=number.clusters,y=fukuyama.dataframe.m1.5$V1)) + geom_line(aes(color="m=2",x=number.clusters,y=fukuyama.dataframe.m2$V1)) + geom_line(aes(color="m=4",x=number.clusters,y=fukuyama.dataframe.m4$V1)) + labs(color="m parameter")+xlab("number of clusters")+ylab("Fukuyama index") + ggtitle("Fukuyama index average per 100 realizations vs number of clusters")+
  scale_x_continuous(breaks=2:20)
```



## Xie-Beni index
Optimum Xie-Beni index has to be minimum
```{r Xie-Beni, cache=FALSE}
xie.dataframe.m1.1 <- ldply(indexes.m1.1$xie.ave)
xie.dataframe.m1.2 <- ldply(indexes.m1.2$xie.ave)
xie.dataframe.m1.4 <- ldply(indexes.m1.4$xie.ave)
xie.dataframe.m1.5 <- ldply(indexes.m1.5$xie.ave)
xie.dataframe.m2 <- ldply(indexes.m2$xie.ave)
xie.dataframe.m4 <- ldply(indexes.m4$xie.ave)



#Options to plot the comparisons per m

ggplot() + geom_line(aes(color="m=1.1",x=number.clusters,y=xie.dataframe.m1.1$V1)) +
  geom_line(aes(color="m=1.2",x=number.clusters,y=xie.dataframe.m1.2$V1))+
  geom_line(aes(color="m=1.4",x=number.clusters,y=xie.dataframe.m1.4$V1))+
  geom_line(aes(color="m=1.5",x=number.clusters,y=xie.dataframe.m1.5$V1)) + geom_line(aes(color="m=2",x=number.clusters,y=xie.dataframe.m2$V1)) + labs(color="m parameter")+ geom_line(aes(color="m=4",x=number.clusters,y=xie.dataframe.m4$V1)) + xlab("number of clusters")+ylab("Xie Beni index") + ggtitle("Xie Beni index average per 100 realizations vs number of clusters")+  scale_y_continuous(breaks=seq(0,0.001,0.0001),limits=c(0,0.0012))+scale_x_continuous(breaks=2:20)
```



## Partition coefficient index
Optimum Partition coefficient index has to be maximum
```{r part.coeff, cache=FALSE}
part.coeff.dataframe.m1.1 <- ldply(indexes.m1.1$part.coeff.ave)
part.coeff.dataframe.m1.2 <- ldply(indexes.m1.2$part.coeff.ave)
part.coeff.dataframe.m1.4 <- ldply(indexes.m1.4$part.coeff.ave)
part.coeff.dataframe.m1.5 <- ldply(indexes.m1.5$part.coeff.ave)
part.coeff.dataframe.m2 <- ldply(indexes.m2$part.coeff.ave)
part.coeff.dataframe.m4 <- ldply(indexes.m4$part.coeff.ave)



#Options to plot the comparisons per m

ggplot() + geom_line(aes(color="m=1.1",x=number.clusters,y=part.coeff.dataframe.m1.1$V1)) +
  geom_line(aes(color="m=1.2",x=number.clusters,y=part.coeff.dataframe.m1.2$V1)) +
  geom_line(aes(color="m=1.4",x=number.clusters,y=part.coeff.dataframe.m1.4$V1)) +
  geom_line(aes(color="m=1.5",x=number.clusters,y=part.coeff.dataframe.m1.5$V1)) + geom_line(aes(color="m=2",x=number.clusters,y=part.coeff.dataframe.m2$V1)) + geom_line(aes(color="m=4",x=number.clusters,y=part.coeff.dataframe.m4$V1)) + labs(color="m parameter")+xlab("number of clusters")+ylab("Partition coefficient index") + ggtitle("Partition coefficient index average per 100 realizations vs number of clusters")+scale_x_continuous(breaks=2:20)
```



## Partition entropy index
Optimum Partition entropy index has to be minimum
```{r part.ent, cache=FALSE}
part.ent.dataframe.m1.1 <- ldply(indexes.m1.1$part.ent.ave)
part.ent.dataframe.m1.2 <- ldply(indexes.m1.2$part.ent.ave)
part.ent.dataframe.m1.4 <- ldply(indexes.m1.4$part.ent.ave)
part.ent.dataframe.m1.5 <- ldply(indexes.m1.5$part.ent.ave)
part.ent.dataframe.m2 <- ldply(indexes.m2$part.ent.ave)
part.ent.dataframe.m4 <- ldply(indexes.m4$part.ent.ave)


ggplot() + geom_line(aes(color="m=1.1",x=number.clusters,y=part.ent.dataframe.m1.1$V1)) +
  geom_line(aes(color="m=1.2",x=number.clusters,y=part.ent.dataframe.m1.2$V1))+
geom_line(aes(color="m=1.4",x=number.clusters,y=part.ent.dataframe.m1.4$V1))+
geom_line(aes(color="m=1.5",x=number.clusters,y=part.ent.dataframe.m1.5$V1)) + geom_line(aes(color="m=2",x=number.clusters,y=part.ent.dataframe.m2$V1)) + geom_line(aes(color="m=4",x=number.clusters,y=part.ent.dataframe.m4$V1)) + labs(color="m parameter")+xlab("number of clusters")+ylab("Partition entropy index") + ggtitle("Partition entropy index average per 100 realizations vs number of clusters")+scale_x_continuous(breaks=2:20)
```


## Calinski-Harabasz index
Calinski-Harabasz index has to be maximum
```{r calinski, cache=FALSE}
calinski.dataframe.m1.1 <- ldply(indexes.m1.1$calinski.ave)
calinski.dataframe.m1.2 <- ldply(indexes.m1.2$calinski.ave)
calinski.dataframe.m1.4 <- ldply(indexes.m1.4$calinski.ave)
calinski.dataframe.m1.5 <- ldply(indexes.m1.5$calinski.ave)
calinski.dataframe.m2 <- ldply(indexes.m2$calinski.ave)
calinski.dataframe.m4 <- ldply(indexes.m4$calinski.ave)


ggplot() + geom_line(aes(color="m=1.1",x=number.clusters,y=calinski.dataframe.m1.1$V1)) +
  geom_line(aes(color="m=1.2",x=number.clusters,y=calinski.dataframe.m1.2$V1)) +
  geom_line(aes(color="m=1.4",x=number.clusters,y=calinski.dataframe.m1.4$V1)) +geom_line(aes(color="m=1.5",x=number.clusters,y=calinski.dataframe.m1.5$V1)) + geom_line(aes(color="m=2",x=number.clusters,y=calinski.dataframe.m2$V1)) + geom_line(aes(color="m=4",x=number.clusters,y=calinski.dataframe.m4$V1)) +labs(color="m parameter")+xlab("number of clusters")+ylab("Calinski-Harabasz index") + ggtitle("Calinski-Harabasz index average per 100 realizations vs number of clusters")+scale_x_continuous(breaks=2:20)
```

## Optimum cluster number conclusion
The best number of clusters to develop the fuzzy clustering over this dataset

